\chapter{Direct Match Questions}
\label{ch:direct_match_questions}

For answering the research questions of this Master's Thesis the \textit{Effectiveness} part of \ac{OPS} was filled in by the employees of company A. Some of the direct match questions though exist in both \textit{Capability} and \textit{Effectiveness} parts. As a result the questions following below are separated based on which \ac{OPS} part they belong.

\begin{longtable} {| p{1.5cm} | p{3.6cm} | p{3.6cm} | p{3cm} | p{1.1cm} |} \caption{Direct Match Questions (OPS Effectiveness)} \\ \hline
	\label{table:direct_match_table_effectiveness} 	
		\textbf{Group} & \textbf{OPS} & \textbf{TAA}  & \textbf{PAM} & \textbf{Figure}\\ \hline \endhead
		\label{G1} G1 & To what extent are the stories fully estimated when added to the iteration backlog? & Stories sufficiently elaborated prior to planning meetings & & \ref{fig:iid_heat} \\ \hline
		\label{G2} G2 & To what extent are the features prioritized when they are added to the product backlog? & Backlog prioritized and ranked by business value & & \ref{fig:pb_heat} \\ \hline
		\label{G3} G3 & To what extent is software released frequently? & The team has small and frequent releases & We implemented our code in short iterations & \ref{fig:sfpr_heat} \\ \hline
		\label{G4} G4 & To what extent are the stories prioritized when added to the iteration backlog? & Iteration backlog ranked by priority & & \ref{fig:iptr_heat2} \\ \hline
		\label{G5} G5 & To what extent is the time allocated for the iteration planning meetings utilized effectively? & Iteration planning meeting attended and effective & & \ref{fig:iptr_heat3}\\ \hline
		\label{G6} G6 & To what extent is the length of an iteration 4 weeks or less? & Iterations are no more than four weeks in length & & \ref{fig:iptr_heat4} \\ \hline
		\label{G7} G7 & To what extent are the iterations timeboxed? & Iterations are of a consistent fixed length &  & \ref{fig:iptr_heat1} \\ \hline
		\label{G8} G8 & To what extent do the team members determine, plan, and manage their day-to-day activities under reduced or no supervision from the management? & Team defines, estimates, and selects their own work (stories and tasks) &  & \ref{fig:sot_heat} \\ \hline
		\label{G9} G9 & To what extent does the team effectively complete the work that they have committed to? & Team members complete commitments & & \ref{fig:ade_heat}\\ \hline
		\label{G10} G10 & To what extent is the time allocated for the release planning meetings utilized effectively? & Release planning meeting attended and effective & & \ref{fig:hbc_heat}\\ \hline
		\label{G11} G11 & To what extent did the developers provide adequate code coverage from the tests? & 100\% automated unit test coverage & & \ref{fig:tdd_heat} \\ \hline
		\label{G12} G12 & To what extent do the teams implement refactoring? & Refactoring is continuous & & \ref{fig:ref_heat} \\ \hline
		\label{G13} G13 & To what extent do teams use appropriate tools for version control and management? & Source control system exists & & \ref{fig:scm_heat} \\ \hline
		\label{G14} G14 & To what extent are automated test suites developed? & Automated acceptance tests & & \ref{fig:ci_heat1}\\ \hline
		\label{G15} G15 & To what extent do the customers establish the priorities of the features? & & The customer picked the priority of the requirements in the iteration plan & \ref{fig:cli_heat}\\ \hline
		\label{G16} G16 & & Identical builds for developers' workstations & Developers had the most recent version of code available & \ref{fig:ci_heat2} \\ \hline
		\label{G17} G17 & & Developers integrate code multiple times per day & The team integrated continuously & \ref{fig:ci_heat3}\\ \hline
		\end{longtable}

\begin{table} [H]
	\begin{tabular}{{| p{4cm} | p{4cm} | p{4cm} |}}
		\hline
		\textbf{OPS} & \textbf{TAA}  & \textbf{PAM} \\ \hline	
		Is the physical environment conducive to supporting high bandwidth communication? & Team works in a physical environment that fosters collaboration & \\ \hline
		To what extent is the time allocated for the daily progress tracking meetings utilized effectively? & Daily stand up on time, fully attended and effectively communicates & \\ \hline
		Are the developers expected to write unit tests first for their code? & Unit tests written before development & \\ \hline
		Is it expected that each team creates and adopts a set of coding standards? & Coding standards exist and applied & \\ \hline
		Is it expected that the code be kept up to date? & Developers had the most recent version of code available & Identical builds for developers’ workstations \\ \hline
		Are the team members expected to integrate their code every few hours? & Developers integrate code multiple times per day & The team integrated continuously \\ \hline
	\end{tabular}
\caption{Direct Match Questions (OPS Capability)}
\label{table:table:direct_match_table_capability}
\end{table}	

