\chapter{OPS, PAM, TAA}
\label{ch:ops_pam_taa}

\section{Capability}

\begin{itemize}
	\item Refactoring
		\begin{itemize}
			\item Support for Refactoring 
				\begin{itemize}
					\item Is refactoring an expected activity?
					\item Is it feasible to implement code refactoring?
					\item Is it feasible to implement architecture refactoring?
				\end{itemize}
			\item Buy-in for Refactoring
				\begin{itemize}
					\item Are the teams receptive to implementing refactoring?
					\addition Are the teams permitted to refactor anywhere in the code base?
					\item Is the management receptive to supporting refactoring efforts?
				\end{itemize}
			\item Minimizing Technical Debt
				\begin{itemize}
					\item Is it expected that a well-defined process be adopted to minimize technical debt?
					\item Is it expected that a well-defined process be adopted to manage technical debt?
					\item Is minimizing technical debt a high priority activity?
				\end{itemize}
		\end{itemize}	
%---------------------------------------------------------------------------	
	\item Test First Development
		\begin{itemize}
			\item Process Support for Test-First Development
				\begin{itemize}
					\item Is test-first development an expected activity?
					\item Are the customers expected to specify the acceptance criteria for the features and stories before the developers begin coding?
					\addition Are the developers expected to write acceptance tests first for their code?
				\end{itemize}
		\end{itemize} 
		\begin{itemize}
			\item Tool Support for Test First Development
				\begin{itemize}
					\item Do appropriate testing tools exist?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Unit Testing
				\begin{itemize}
					\item Are the developers expected to write unit tests first for their code?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Retrospection
		\begin{itemize}
			\item Support for Retrospection
				\begin{itemize}
					\item Is retrospection an expected activity?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Tool Support for Retrospection
				\begin{itemize}
					\item Are tools available for recording the outcomes of the retrospective meetings?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item Distribution of expertise
		\begin{itemize}
			\item Appropriate team composition
				\begin{itemize}
					\item Is a scheme for appropriate team composition defined?
					\item Are the requisite skillsets for particular projects identified upfront?
					\item Is it expected that the right people be chosen to accomplish the tasks?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item Configuration Management
		\begin{itemize}
			\item Tool Support for Configuration Management
				\begin{itemize}
					\item Do tools for version control and management exist?
				\end{itemize}
			\item Support for Configuration Management
				\begin{itemize}
					\item Is it expected that the code be kept up to date?
					\item Is it expected that the tests be kept up to date?
					\item Is it expected that the builds be kept up to date?
					\item Is it expected that the release infrastructure be kept up to date?
					\item Is it expected that the documentation be kept up to date?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Adherence to standards
		\begin{itemize}
			\item Identifying features
				\begin{itemize}
					\item Is it expected that well-defined techniques be used to identify the features?
					\end{itemize}
			\item Estimation
				\begin{itemize}
					\item Is it expected that a well-defined approach to estimating the amount of work to be done during each release cycle and iteration be used?
				\end{itemize}
			\item Requirements Prioritization
				\begin{itemize}
					\item Is it expected that a well-defined approach to prioritizing bugs/enhancements, and tasks be used?
				\end{itemize}	
			\item Feature Decomposition
				\begin{itemize}
					\item Is it expected that a mechanism for decomposing the selected features to be developed during the current release cycle into bugs/enhancements be defined?
				\end{itemize}
			\item Coding standards
				\begin{itemize}
					\item Is it expected that each team creates and adopts a set of coding standards?
					\item Is it expected that practices such as pair-programming, collective code ownership be adopted or automated tools be used to ensure adherence to the set standards?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Continuous Integration
		\begin{itemize}
			\item Tool Support for Continuous Integration
				\begin{itemize}
					\item Do automated test suites exist?
					\item Does the requisite test environment exist?
					\item Do appropriate configuration management systems exist?
				\end{itemize}
			\item Process Support for Continuous Integration
				\begin{itemize}
					\item Is continuous integration an expected activity?
					\item Are the team members expected to integrate their code every few hours?
					\item Is it expected that the builds, tests, and other release infrastructure be kept up to date?
					\item Is it expected that automated test suites be developed?
					\item Is it expected that the build process be automated?
				\end{itemize}
			\item Buy-in for Continuous Integration
				\begin{itemize}
					\item Are the teams receptive to implementing continuous integration?
				\end{itemize}
			\item Story Completeness
				\begin{itemize}
					\item Is it expected that the criteria for Done/Done be specified upfront?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Self-managing teams
		\begin{itemize}
			\item Team Empowerment
				\begin{itemize}
					\item Are the team members expected to be involved in determining, planning, and managing their day-to-day activities?
				\end{itemize}
			\item Ownership
				\begin{itemize}
					\item Are the team members expected to demonstrate individual or collective code ownership? 
				\end{itemize}
			\item Performance Expectations
				\begin{itemize}
					\item Is there a set of performance expectations that are agreed upon by the team and the management?
				\end{itemize}
%			\addition Size
%				\begin{itemize}
%					\addition Is it expected the team be smaller than 15 people?
%				\end{itemize}
			\indicatorAddition Communication
				\begin{itemize}
					\addition Are the team members expected to have a common language?
				\end{itemize}
			\indicatorAddition{System Administration}
				\begin{itemize}
					\addition Are the team members expected to have administrative access to their own workstations?
					\addition Are the team members expected to have control over their development environment?	
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Continuous Feedback
		\begin{itemize}
			\item Customer Feedback
				\begin{itemize}
					\item Does the process define a mechanism for the customers to provide feedback?
				\end{itemize}			
		\end{itemize}
		\begin{itemize}
			\item Customer Acceptance
				\begin{itemize}
					\item Is it expected that the acceptance testing occur before the end of a release cycle?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item High-bandwidth communication
		\begin{itemize}
			\item On-site Customer
				\begin{itemize}
					\item Are the customers available onsite to answer questions and provide continuous feedback? 
					\item In the absence of an onsite customer, do the customers provide feedback via other means? 
				\end{itemize}	
			\item Scheduling
				\begin{itemize}
					\item Is it expected that time be allocated for Release Planning?
					\item Is it expected that time be allocated for Iteration Planning?
					\item Is it expected that time be allocated for Retrospection? 
					\item Is it expected that time be allocated for Daily Progress Tracking meetings?
				\end{itemize}
			\item Inter- and intra-team communication
				\begin{itemize}
					\item Is it expected that team members communicate and collaborate with their colleagues?
					\item Do the teams have access to requisite tools to support inter- and intra-team communication?
				\end{itemize}
			\item Physical environment
				\begin{itemize}
					\item Is the physical environment conducive to supporting high bandwidth communication?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Client-driven Iterations
		\begin{itemize}
			\item Identifying and prioritizing features
				\begin{itemize}
					\item Are the customers expected to be involved in identifying the features?
					\item Are the customers expected to establish the priorities of the features?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Short delivery cycles
		\begin{itemize}
			\item Development time-frames
				\begin{itemize}
					\item Is it expected that the product be developed over short delivery cycles? For example, a product increment should be released every 6 - 12 months and iterations last for four weeks or less.
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Iterative Progression
		\begin{itemize}
			\item Planning
				\begin{itemize}
					\item Is the team expected to plan for each iteration?
					\addition Is it expected that the team velocity is used for planning?
				\end{itemize}
			\item Estimation Authority
				\begin{itemize}
					\item Are the developers expected to estimate the time required to complete each story?
				\end{itemize}
			\item Estimation
				\begin{itemize}
					\item Is it expected that a well-defined approach to estimating the amount of work to be done during each release cycle and iteration be used?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Incremental Development
		\begin{itemize}
			\item Estimation Authority
				\begin{itemize}
					\item Are the developers expected to estimate the time required to complete each story?
				\end{itemize}
			\item Requirements Management
				\begin{itemize}
					\item Are tools available for managing the bugs/enhancements?
				\end{itemize}
			\item Identifying and prioritizing features
				\begin{itemize}
					\item Are the customers expected to be involved in identifying the features?
					\item Are the customers expected to establish the priorities of the features?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\strategyAddition Velocity
		\begin{itemize}
			\indicatorAddition Progress Estimation
				\begin{itemize}
					\addition Is it expected that the progress is track by a burn down chart and by measuring velocity?
				\end{itemize}
		\end{itemize}
%----------------------------------------------------------------------------
	\item Evolutionary Requirements
		\begin{itemize}
			\item Minimal Big Requirements Up Front and Big Design Up Front
				\begin{itemize}
					\item Is it expected that only high level features be identified upfront?
					\item Is it expected that an evolutionary approach to architecting the system be followed as opposed to creating the architecture upfront?
				\end{itemize}
			\item Just-In-Time Refinement
				\begin{itemize}
					\item Is it expected that the requirements be determined and refined just-in-time?
				\end{itemize}
			\item Feature Decomposition
				\begin{itemize}
					\item Is it expected that a mechanism for decomposing the selected features to be developed during the current release cycle into stories be defined?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Minimal Documentation
		\begin{itemize}
			\item Tool Support for Minimal Documentation
				\begin{itemize}
					\item Do tools for maintaining documentation exist?
				\end{itemize}
			\item Process support for Minimal Documentation
				\begin{itemize}
					\item Is it expected that minimal documentation be maintained?
				\end{itemize}
			\item Buy-in for Minimal Documentation
				\begin{itemize}
					\item Are the teams receptive to maintaining minimal or just-enough documentation?
				\end{itemize}
		\end{itemize}
\end{itemize}





\section{Effectiveness}

\begin{itemize}
	\item Refactoring 
		\begin{itemize}
			\item Minimizing Technical Debt 
				\begin{itemize}
					\item To what extent do the teams manage technical debt? 
					\item To what extent do the teams minimize technical debt when developing new systems? 
					\item To what extent does the system and the development environment allow Technical Debt to be minimized? 
				\end{itemize}
			\item Buy-in for Refactoring 
				\begin{itemize}
					\item To what extent does the management support the implementation of refactoring? 
					\item To what extent do the teams implement refactoring? 
					\addition To what extent are the teams permitted to refactor anywhere in the code base?			
					\addition To what extent were there enough unit tests and automated system test to allow developers to safely refactor?					
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Test First Development
		\begin{itemize}
			\item Code coverage
				\begin{itemize}
					\item To what extent did the developers provide adequate code coverage from the tests?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Customer Satisfaction
				\begin{itemize}
					\item To what extent is the product developed so far in-sync with the customers' needs and expectations?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Testing first
				\begin{itemize}
					\item To what extent do developers write tests first before writing code?
					\item To what extent are the test plans created before the developers start coding?
					\addition To what extent was the implemented code written to pass the test case?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Retrospection
		\begin{itemize}
			\item Retrospective meetings
				\begin{itemize}
					\item To what extent are the retrospectives applied?				
				\end{itemize}
			\item Process Outcomes for Retrospection
				\begin{itemize}
					\item To what extent were practices that worked well during the iteration or the release cycle and hence should be used in the future identified?
					\item To what extent were practices that did not yield the expected results and hence should be discontinued identified?
					\item To what extent were new practices that may better suit the team's needs identified?
					\addition To what extent were the retrospectives helpful for seeing what worked well in the past iterations?
					\addition To what extent were the retrospectives helpful for seeing what should be improved in the upcoming iterations?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Retrospective goals
				\begin{itemize}
					\item To what extent were the retrospective goals set during the previous iteration met?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\indicatorAddition Team
				\begin{itemize}
					\addition To what extent did team members participate in the retrospective meetings?
					\addition To what extent does the team inspect and adapt the overall process?
					\addition To what extent does the team continuously improve the iteration plan?
					\addition To what extent does the team continuously improve the release plan?
				\end{itemize}
		\end{itemize}
		%\begin{itemize}
		%	\addition Outcomes
				%\begin{itemize}
					
				%	\addition To what extent did the points improve from the previous retrospectives?
				% \addition To what extent were important points for improvement assigned to responsible individuals?
			%	\end{itemize}	 
		%\end{itemize}
%---------------------------------------------------------------------------
	\item Distribution of expertise 
		\begin{itemize}
			\item Process Outcomes for Distribution of Expertise
				\begin{itemize}
					\item To what extent do the team members have the requisite expertise to complete the tasks assigned to them? 
					\item To what extent is the work assigned to the team members commensurate with their expertise? 
					\item To what extent does the team effectively complete the work that they have committed to? 
					\item To what extent do the teams have members in leadership positions that can guide the others? 
					\item To what extent do the teams not rely on knowledge external to their teams? 
					\addition To what extent is the team cross-functional?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Configuration Management
		\begin{itemize}
			\item Project Environment for Configuration Management
				\begin{itemize}
					\item To what extent do teams use appropriate tools for version control and management?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item Adherence to standards
		\begin{itemize}
			\item Estimation
				\begin{itemize}
					\item To what extent are the estimates for the amount of work to be done during each iteration accurate?
				\end{itemize}
			\item Coding Standards
				\begin{itemize}
					\item To what extent do the team members agree with the set coding standards? 
					\item To what extent do the team members adhere to the set coding standards?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Continuous Integration
		\begin{itemize}
			\item Project Environment for Continuous Integration 
				\begin{itemize}
					\item To what extent are automated test suites developed?
					\item To what extent are the code bases not shared?
				\end{itemize}
			\indicatorAddition Process Support for Continuous Integration
				\begin{itemize}
							\addition To what extent do the team members integrate their code per day?
				\end{itemize}
			\item Story Completeness
				\begin{itemize}
					\item To what extent has each story been coded? 
					%\item To what extent has each story been unit tested? 
					\addition To what extent has each story been unit tested successfully?
					\item To what extent has each story been refactored? 
					\item To what extent has each story been checked into the code base? 
					\item To what extent has each story been integrated with the existing code base? 
					\item To what extent has each story been reviewed? 
					\item To what extent has each story been accepted by the customer? 
					\addition To what extent were the stories accepted and demonstrated on integrated build?
				\end{itemize}
			\item Daily/Frequent builds
				\begin{itemize}
					\item To what extent do automated builds run one or more times everyday?
					\addition To what extent are the automated builds successful?
					\addition To what extent test reports for automated were unit tests  systematically used to capture the bugs?
				\end{itemize}
		\end{itemize}

%---------------------------------------------------------------------------		
	\item Self-managing teams
		\begin{itemize}
			\item Team Empowerment
				\begin{itemize}
					\item To what extent do the team members determine the amount of work to be done? 
					\item To what extent do the team members take ownership of work items? 
					\item To what extent do the team members hold each other accountable for the work to be completed? 
					\item To what extent do the team members ensure that they complete the work that they are accountable for?
				\end{itemize}
			\item Autonomy
				\begin{itemize}
					\item To what extent do the team members determine, plan, and manage their day-to-day activities under reduced or no supervision from the management? 
					\item To what extent do the developers form ad-hoc groups to determine and refine requirements just-in-time?
					\addition To what extend does the team self-police and reinforce the practices and rules?
				\end{itemize}
			\item Management support
				\begin{itemize}
					\item To what extent does the management support the self-managing nature of the teams?
				\end{itemize}
			\indicatorAddition Commitment
				\begin{itemize}
					\addition To what extent is the team dedicated to the release?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------	
	\item Continuous Feedback	
		\begin{itemize}
			\item Customer Feedback
				\begin{itemize}
					\item To what extent do the customers provide feedback to the business and the development team?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Customer Satisfaction
				\begin{itemize}
					\item To what extent is the product developed so far in-sync with the customers' needs and expectations?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\indicatorAddition Customer Acceptance
				\begin{itemize}
					\addition To what extent were customer acceptance tests applied?
					\addition To what extent did the customer focus on acceptance tests to determine what had been accomplished?
					\addition To what extent were the acceptance tests the ultimate way to verify system functionality and customer requirements?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item High-bandwidth communication
		\begin{itemize}
			\indicatorAddition Customer Access
				\begin{itemize}
					\addition To what extent were the responses from the customer in a timely manner?
					\addition To what extent was the feedback from the customer clear and clarified the requirements or open issues to the developers?
				\end{itemize}
		\end{itemize}
		\begin{itemize}
			\item Customer Satisfaction
				\begin{itemize}
					\item To what extent is the product developed so far in-sync with the customers' needs and expectations?
				\end{itemize}
			\item Scheduling
				\begin{itemize}
					\item To what extent is the time allocated for the release planning meetings utilized effectively? 
					\item To what extent is the time allocated for the iteration planning meetings utilized effectively?
					\item To what extent is the time allocated for the retrospective meetings utilized effectively? 
					\item To what extent do the scheduled meetings (except the daily progress tracking meetings) begin and end on time? 
					\item To what extent do the meetings (except the daily progress tracking meetings) take place as scheduled? 
				\end{itemize}
			\indicatorAddition Daily progress tracking meetings
				\begin{itemize}
					\item To what extent is the time allocated for the daily progress tracking meetings utilized effectively? 
					\addition To what extent were daily progress tracking meetings up to 15 minutes?
					\addition To what extent did all relevant technical issues or organizational impediments came up in the daily progress tracking meetings?
					\addition To what extent were the daily progress tracking meetings the quickest way to notify the other team members about problems?
					\addition To what extent did team members offer to help when people reports problems in the daily progress tracking meetings?
					\addition To what extent was the daily progress tracking meeting on time?
				\end{itemize}
			\item Inter- and intra-team communication
				\begin{itemize}
					\item To what extent does open communication prevail between the business and the development team? 
					\item To what extent does open communication prevail between the manager and the developers and testers? 
					\item To what extent does open communication prevail between the developers and the testers? 
					\item To what extent does open communication prevail among the developers? 
					\item To what extent does open communication prevail between the external customer/user and the business? 
					\item To what extent does open communication prevail between the external customer/user and the development team? 
					\item To what extent does open communication prevail between members of different teams?
					\addition To what extent does the team have an effective channel for obstacle escalation?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item Client-driven Iterations
		\begin{itemize}
			\item Requirements Prioritization
				\begin{itemize}
					\item To what extent do the customers establish the priorities of the story?
					\addition To what extent are the features reprioritized when the scope could not be implemented due to constraints?
				\end{itemize}
			\item Customer Satisfaction
				\begin{itemize}
					\item To what extent is the product developed so far in-sync with the customers' needs and expectations?
				\end{itemize}
			\item Customer Requests
				\begin{itemize}
					\item To what extent are the changes requested by the customers accommodated?
				\end{itemize}			
		\end{itemize}
%---------------------------------------------------------------------------	
	\item Short delivery cycles
		\begin{itemize}
			\item Development time-frames
				\begin{itemize}
					\item To what extent is software released frequently? (length of a release cycle is one year or less)
					\item To what extent is software released frequently? (length of an iteration is four weeks or less)
				\end{itemize}
			\item Customer Satisfaction
				\begin{itemize}
					\item To what extent is the product developed so far in-sync with the customers' needs and expectations?
				\end{itemize}
			\item Roll-backs
				\begin{itemize}
					\item To what extent are the deployments not rolled back?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item Iterative Progression
		\begin{itemize}
			\item Estimation
				\begin{itemize}
					\item To what extent are the estimates for the amount of work to be done during each iteration accurate?
					\addition To what extent were the effort estimates for the iteration scope items modified by the team members?
					\addition To what extent did the team discuss when effort estimates differed?  
					\addition To what extent did the team reduce the scope than delaying the deadline?
					\addition To what extent did team members take part in defining the amount of work to be done?
					\addition To what extent did the concerns of the team members about reaching the iteration goals were taken into consideration?
					\addition To what extent did the team discuss the acceptance criteria during the iteration planning?
					\addition To what extent did the team members actively participate during iteration planning meetings?
				\end{itemize}
			\item Iteration length
				\begin{itemize}
					\item To what extent are the iterations timeboxed?
					\item To what extent is the length of an iteration 4 weeks or less?
				\end{itemize}
			\item Requirements Management for Iterations
				\begin{itemize}
					\item To what extent is an iteration backlog maintained?
					\addition To what extent do the team members manage the iteration backlog? 
					\item To what extent are the stories fully estimated when added to the backlog?
					\item To what extent are the stories prioritized when added to the backlog?
				\end{itemize}
			\indicatorAddition Product
				\begin{itemize}
					\addition To what extent was the product shippable at the end of the iteration?
					\addition To what extent was the working software the primary measure for project progress?
					\addition To what extent did the delivered software meet the quality requirements of production code at the end of the iteration?
					\addition To what extent is the progress tracked by feature acceptance?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------		
	\item Incremental Development
		\begin{itemize}
			\item Requirements Management for Releases
				\begin{itemize}
					\item To what extent is a product backlog maintained?
					\item Backlog estimated at gross level
					\item To what extent are the features prioritized when they are added to the product backlog?
					\item To what extent are the features fully estimated before they are added to the product backlog?
					\addition To what extent is a release backlog maintained?
					\addition To what extent is release backlog estimated at plan level 
					\addition To what extent are the features prioritized when they are added to the release backlog?
				\end{itemize}
			\item Timeboxing Releases
				\begin{itemize}
					\item To what extent are the release cycles timeboxed?
					\item To what extent are only a subset of the identified features developed during a release cycle?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\strategyAddition Velocity
		\begin{itemize}
			\indicatorAddition Pace
				\begin{itemize}
					\addition To what extent does the team work at a sustainable pace?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Evolutionary Requirements
		\begin{itemize}
			\item Requirements Reprioritization 
				\begin{itemize}
					\item To what extent are the features reprioritized as and when new features are identified?
				\end{itemize}
			\item Customer Requests
				\begin{itemize}
					\item To what extent are the changes requested by the customers accommodated?
					\addition To what extent is a requirement regarded as finished until its acceptance tests (with the customer) has passed?
				\end{itemize}
			\item Minimal Big Requirements Up Front and Big Design Up Front
				\begin{itemize}
					\item To what extent are only the high level features identified upfront?
					\item To what extent are the architecture requirements allowed to evolve over time?
				\end{itemize}
		\end{itemize}
%---------------------------------------------------------------------------
	\item Minimal Documentation
		\begin{itemize}
			\item Maintaining documentation 
				\begin{itemize}
					\item To what extent is minimal documentation supported by teams?
					\item To what extent is minimal documentation created/developed?
					\item To what extent is minimal documentation recorded/archived?
					\item To what extent is minimal documentation maintained?
				\end{itemize}
		\end{itemize}
\end{itemize}
