
\section{Research Questions}

\begin{enumerate}
	\item Will PAM, TAA and OPS yield similar results?
	%by changing into "Roman" you will get capital letters
	\begin{enumerate}[label*=\arabic*.]
  		\item Does convergent validity exist among the tools?
  		\item Will the questions that are exactly the same among the tools yield the same results?
		\item What is the coverage of agile practices among the tools?
	\end{enumerate}	
  	\item Can the tools be combined in a way that will provide a better approach to measuring agility?
\end{enumerate}

\clearpage

%------------------------------------------------


\section{Research Methodology}

%------------------------------------------------

\subsection{Study in Company $A$}

United States company which activates in the Point Of Sales (POS) area. \\
Development and QA departments (4 mixed teams). \\

\subsection{Methodology $A$}
The analysis made by Koch \cite{koch2005agile} was used for identifying the methodologies and practices Company $A$ uses.

\subsection{Data Collection}

Company $A$ employees were asked to fill in the surveys created by PAM, TAA and OPS (Effectiveness part) during a 3-week period. The surveys were on 1-7 Likert scale except from the \textit{Collocation} practice which was on a Likert scale 1-5.
Practices which were not used by Company $A$ were excluded from the surveys.

\clearpage

%------------------------------------------------

\subsection{Data Preparation}

\subsubsection{Problem}
All the tools have different amount of questions and cover different practices

\subsubsection{Solution}
\begin{enumerate}
	\item Mapping of practices between tools --- OPS covers more practices
	\item Mapping of questions based on the OPS practices
\end{enumerate}

\clearpage

%------------------------------------------------

\subsection{Data Analysis}

\begin{table} [H]
	\begin{tabular}{| c | c | c | c | c |} \hline
	\textbf{Practice} & \textbf{Participants} & \textbf{PAM} & \textbf{TAA} & \textbf{OPS} \\ \hline
	\multirow{3}{*}{Practice1} & Participant1 & Score1 & Score1 & Score1 \\ \hhline{~----}
	& \vdots & \vdots & \vdots  & \vdots \\ \hhline{~----}
	& ParticipantN & ScoreN & ScoreN & ScoreN \\ \hline
	\end{tabular}
	\caption{Collected Data Structure}
	\label{table:data_structure}
\end{table}

\clearpage

\begin{itemize}
	\item Correlations ({\footnotesize Convergent Validity Establishment})
	\item Direct Match Questions Analysis
	\item Tools' Agile Practices Coverage
\end{itemize}

\clearpage

\subsubsection{Correlations}

\begin{itemize}
	\item Use the practices covered by each tool and see if they correlate with the same practices from the other two tools
	\item Use ``Spearman's rank correlation coefficient"
\end{itemize}

\clearpage

\subsubsection{Direct Match Questions Analysis}

\begin{itemize}
	\item Identified which questions were the same among the tools
	\item ``Mann-Whitney U test" and ``Kruskal-Wallis one-way analysis of variance" for statistical tests
\end{itemize}

The hypothesis is

\begin{itemize}[label={}]
	\item $H_0$: \textit{There is no difference between the groups of the same questions}
	\item $H_1$: \textit{There is a difference between the groups of the same questions}
\end{itemize}

\clearpage

\subsubsection{Tools' Agile Practices Coverage}

Checked which of the tools cover more agile practices and have more questions for a practice

\begin{itemize}
	\item and were the most popular according to two case studies \cite{Williams_Microsoft, laurie_williams}.
	\item and did not exist or were not popular in the case studies.
\end{itemize}

\clearpage

%------------------------------------------------